\documentclass[12pt]{article}
\title{Risks Involved In The Manual Transaction and Record Keeping System At Makumbi's Whole Sale Shop}
\begin{document}
\maketitle
\section{Abstract}
Transaction processing system plays a vital role in financial transactions of a given business organisation. When evaluating risks, it is more effective to analyse potentail risks.Therefore it is important for an organisation to manage its risks, enhance its values and improve business perfomance.More so the kind of system used to process the transactions also greatly determines the rate at which the business is exposed to risk. 
\section{Introduction}
Transaction processing is information processing that is divided into individual operations, called transaction.With the existing manual transaction information system at Makumbi's Whole Sale Shop,there are high chances of losing track of some transaction made.This may lead to a decline the profits made and to some extent it may lead to the down fall of the business. \\

\subsection{Problem statement}
Manual processing can be a very tricky and mind numbing process. Data entry consists of transferring data from a physical state into a digital state with other various procedures involved as well. In recent times, where technology is at an all-time high, there is less and less need for manual data entry because everything is being done through computers and advanced technology. By using new technology it decreases and solves the problems of manual data entry.
\subsubsection{Too Much Money}
Manual data entry takes a lot of money to conduct efficiently. Employees need to be properly trained for any kind of data entry and training is a huge amount of time and money for the company.
\subsubsection{Human Error}
The next really important problem in relation to data entry is human error. Everyone knows that humans are not perfect and there are going to be times when mistakes are made, whether it is spelling, grammar, or punctuation. Using automation will reduce the margin of error.
\subsubsection{Time Consuming}
When entering information manually, it takes up a lot of time, no matter how fast one can type or process information, it will never be as fast as it needs to be. Typing in a lot of information can be tricky and cause individuals to lose focus and this will also add to the time it takes for data entry. Not being fast enough leads to a big delay in data availability
\subsubsection{Misinterpretation}
The last issue with data entry is misinterpretation; this means that because the entries are being conducted by humans there is always room for misunderstanding. Everyone’s mind thinks differently and understands things in different ways and the same goes for data entry.
\subsection{Objectives}
\subsubsection{General objectives}
To develop a transaction information system in order to eliminate the risks involved the manual transaction and record keeping system at Makumbi's whole sale shop.
\subsubsection{Specific objectives}
The primary objective of TPS is to capture, gather, process, and store transactions and to produce useful documents related to routine business activities to managers.
\begin{itemize}
\item To implement a computerized TPS to allow transaction to be processed in a very short period of time and produce timely documents and reports.
\item To ensure that all the data and information stored in databases are always accurate, current, appropriate and up to date.
\end{itemize}






\end{document}
